---
title: Caching with knitr and Rmarkdown
author: Mikey Harper
draft: true
date: '2018-04-19'
slug: caching-with-knitr-and-rmarkdown
categories:
  - R
  - Technical
tags:
  - Reproducible Resaerch
  - R
---

R Markdown is fantastic tool to 


## Caching

It can slow things does if these have to run large computations within your analysis. For example, you may have a 

## Invalidating Cache

One limitation which can create problems with caching is that it is 


https://stackoverflow.com/q/18376008/7347699

As an example, if we have the basic R Markdown file

````markdown
---
output: pdf_document
---

`r ''```{r}
z <- "Title 5"
y <- "Some Text"
x <- "x2"
```


`r ''```{r cars2, cache = TRUE, cache.whatever= list(x, y, z)}
plot(cars, main = z, xlab = x, ylab = y)
```
````



````markdown
---
output: pdf_document
---

`r ''```{r}
z <- "Title 5"
y <- "Some Text"
x <- "x2"
```


`r ''```{r cars2, cache = TRUE, cache.whatever= list(x, y, z)}
plot(cars, main = z, xlab = x, ylab = y)
```
````



---
output: pdf_document
---

```{r}
z <- "Title 5"
y <- "Some Text"
x <- "x2"
```

``

```{r cars2, cache = TRUE, cache.whatever= list(x, y, z)}
plot(cars, main = z, xlab = x, ylab = y)
```


