---
title: Moving website to Hugo
author: Mikey Harper
date: '2018-03-02'
slug: moving-website-to-hugo
categories: []
tags:
  - Web
bibliography: test.bib
---

I have been toying with the idea for a while about setting up a website through Hugo.^[This is a  footnoted]

# Why Consider


One of the best things about Hugo is that the

The guidance for [blogdown](https://bookdown.org/yihui/blogdown/) is really useful.

Below are some of my favourite features:

## Citations



```{r}
knitr::write_bib(c("rmarkdown", "knitr", "leaflet"), file = "test.bib")
```

[@R-knitr]

## Embedding Live Charts

For example, the leaflet [@R-leaflet] package is great for producing interactive maps. Using the following example taken from [here](https://rstudio.github.io/leaflet/), we can create maps in only a few lines of code:

```{r, results = "asis"}
library(leaflet)

m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=-1.396, lat=50.93, popup="The birthplace of R")
m
```

